---
title: 'Using shiny application for interactive analysis of MTCARS dataset: project
  for the ''Developing Data Products'' Coursera class.'
author: "Youri Matiounine"
date: "April 16, 2018"
output:
  beamer_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Description of the shiny application

This application performs a regression of MTCARS dataset to determine if transmission type impacts miles per gallon (MPG). 

The UI allows user to select which variables are used in a regression, and then displays some output from that regression.

Selectable variables are all but AM (which is always used) and MPG (which is being predicted).

Output is a residual plot, and 3 values: AM regression coefficient, its P-value, and STD of the residuals.


## Benefits of using shiny

- Visual presentation of the results
- Immediate response
- Ability to try multiple approaches
- Flexible structure of result output
- Ability to distribute the application to a wide audience


## Sample output

```{r sample}
fit1<-lm(mpg~am+wt,data=mtcars)
plot(resid(fit1)~mtcars$mpg,xlab="MPG",ylab="Residuals",main="Residual Plot")

sf1<-summary(fit1)
print("Increase in MPG for a manual transmission:")
sf1$coefficients[2,1] # coeff of AM variable
print("P-value of impact of a manual transmission on MPG:")
sf1$coefficients[2,4] # P-value of AM variable
print("STD of residuals:")
sf1$sigma # STD of residuals
```

## Conclusion

Shiny allows quick development and deployment of interative applications.

Application developed for this presentation illustrates basic capabilities of shiny, and can be used as a starting point for furhter development.
